---
title: "MarkdownAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries}
library(dplyr)
library(tidyr)


setwd("~/Dropbox/MOOC/Coursera/Data Science Beginner/3. Getting & Cleaning Data/Project/Coursera-GettingCleaningData")
```

# Get Data
Clear out the dataset if it exists
```{bash}
rm -R UCI\ HAR\ Dataset/
```

```{r}
url = 'https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip'

download.file(url,'UCI HAR Dataset.zip')



```

```{bash}
unzip 'UCI HAR Dataset.zip' -d 'UCI HAR Dataset'
```



# Merge
Merges the training and the test sets to create one data set.
```{r Merge}

```


# Extract
Extracts only the measurements on the mean and standard deviation for each measurement.
Uses descriptive activity names to name the activities in the data set
Appropriately labels the data set with descriptive variable names.

```{r Extract}

```

# Tidy
From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r Tidy}

```

