---
title: "MarkdownAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries}
library(dplyr)
library(tidyr)

setwd("~/Dropbox/MOOC/Coursera/Data Science Beginner/3. Getting & Cleaning Data/Project/Coursera-GettingCleaningData")
```

# Get Data
The following steps are for reliably re-aquiring the source data if I do something silly.

Clear out the dataset if it exists
```{bash DelFolder}
<!-- rm -R UCI\ HAR\ Dataset/ -->
```

Download the data from coursera link
```{r Download Data}
# url = 'https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip'
# 
# download.file(url,'UCI HAR Dataset.zip')



```

Unzip it
```{bash Unzip Download}
<!-- unzip 'UCI HAR Dataset.zip' -->
```


# Merge
Merge the training and the test sets to create one data set.
Note that the raw data (contained in the 'Inertial Signals' subdirectories) does not need to be merged as we are not re-performing this stage of the analysis - i.e the pre-processing.
Instead, only the following files need to be merged:
* 'subject_*.txt' 
* 'X_*.txt' 
* 'y_*.txt' 


```{r Get Feature Names}
# Read in the feature names from the file
X_names=read.table('UCI HAR Dataset/features.txt', header = FALSE,
                   sep = " ", col.names=c('feature_id','feature_name'))

# Use a regular expression to get rid of any .'s or -'s or ,'s or ()'s 
# Note - a double escape needed to use \, as \ itself is a special charachter)
# Note - ? used to prevent greedy matching
X_names$feature_name_clean <- gsub("(\\.|-|,|\\(|\\))?", "", X_names$feature_name)

```


```{r Get Activity Names}
# Read activity names to a new table
activity_names=read.table('UCI HAR Dataset/activity_labels.txt', header = FALSE,
                   sep = " ", col.names=c('activity_id','activity_name'))

```


```{r Read in test data}
# Read in the test data
sub_test <- read.table( 'UCI HAR Dataset/test/subject_test.txt', header = FALSE, 
                        sep = " ", col.names=c('Subject'))

# Note the column names are assiged as the feature names at this point
X_test <- read.table('UCI HAR Dataset/test/X_test.txt', header = FALSE, 
                     sep = "", col.names=X_names$feature_name_clean)

# Read the Activity information to a table
y_test <- read.table('UCI HAR Dataset/test/y_test.txt', header = FALSE,
                     sep = " ", col.names=c('Activity'))

```


```{r Read in training data}

# Read in the training data
sub_train <- read.table( 'UCI HAR Dataset/train/subject_train.txt', header = FALSE, 
                        sep = " ", col.names=c('Subject'))

# Note the column names are assiged as the feature names at this point
X_train <- read.table('UCI HAR Dataset/train/X_train.txt', header = FALSE, 
                     sep = "", col.names=X_names$feature_name_clean)

# Read the Activity information to a table                     
y_train <- read.table('UCI HAR Dataset/train/y_train.txt', header = FALSE,
                     sep = " ", col.names=c('Activity'))
```


```{r Merge Data Together}
# Column bind the subject, activity and data for the test data
testdata <- cbind(sub_test,y_test,X_test)
dim(testdata) # Check dimensions
rm(sub_test,y_test,X_test) # Tidy workspace

# Column bind the subject, activity and data for the training data
traindata <- cbind(sub_train,y_train,X_train)
dim(traindata) # Check dimensions
rm(sub_train,y_train,X_train) # Tidy workspace

# Row bind the test & training data together
alldata <- rbind(testdata,traindata)
dim(alldata) # Check dimensions
rm(testdata,traindata)  # Tidy workspace

```



# Extract
Extracts only the measurements on the mean and standard deviation for each measurement.
Uses descriptive activity names to name the activities in the data set
Appropriately labels the data set with descriptive variable names.

```{r Extract}
# Select only data where the column heading contains std, mean, Subject or Activity
# This brings us down to 88 variables

desireddata <- select(alldata, matches('std|mean|Subject|Activity'))


# Change the Activity variable to a factor, applying the labels in 'activity_name' read in from activity_labels.txt - This allows it to be descriptive without taking up unnecesary space.
desireddata$Activity <- factor(desireddata$Activity,
                               labels=activity_names$activity_name)

```

# Tidy
From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r Tidy}
# Group the data by subject, then activity, and then summarise all of the variable columns using the mean for each of the resulting 180 rows.

tidydata <- desireddata %>% 
  group_by(Subject,Activity) %>% 
  summarise_all(funs(m=mean))

# Check the dimensions are as expected (88 vars selected by 30 subjects x 6 activities)
dim(tidydata)

# Write tidied data out to a file
write.table(tidydata, file='TidyData.txt', append=FALSE)
```

